\begin{plainchp}{Acknowledgements}
    \addcontentsline{toc}{chapter}{Acknowledgements}
    
    First, I want to thank my supervisor Professor Andrew J. Higgins for his deep knowledge, mentorship, and support throughout this journey. He gave me and our lab the singular opportunity to pursue graduate studies on advanced space propulsion. In Canada, this is a rare topic of research indeed, but it is only with advances in this field that humanity will be able to reach the stars.

    I'm very grateful to my family and Anna for their support and encouragement during my studies.

    I would like to extend my heartfelt appreciation to the members of the McGill Interstellar Flight Experimental Research Group. Emmanuel Duplay and Siera Riel, in the pursuit of science together, you have given me dear memories that will last a lifetime. Siera helped with many measurements in the lab, including quasi-continuous wave (QCW) and flowing thrust experiments. She also helped with the design of the Version 2 (V2) thruster and produced the drawings of its new parts. I wish Siera and Anthony Côté much success in continuing the work Emmanuel and I have but started.

    Editorial help was provided by Professor Higgins, Emmanuel, Siera, John Kokkalis, and Sebastian Rodriguez. Sebastian helped manufacture the V2 electrodes. Thank you for your knowledge on how to do things in the lab. Thariq Meulendijks did the needle valve $A^*$ calibration and the bubble flow meter experiments and calculations.

    Alain Halbouny, Jade Tabbara, Karl Atallah, Serge Rubeiz, and Shady Tawil designed and assembled the V2 laser-thermal thruster, as well as produced its drawings and renders. Thank you to Meisam Aghajani, Mathieu Beauchesne, Ramnarine Harihar (Harry), and Andy Hofmann, the machinists who built V2. Without it, we would not have the experimental insights we have today.

    Outside the lab, I want to acknowledge the colleagues that helped make my short stay at McGill even more enjoyable and memorable: Ali Al Abed, Niloy Barua, Caileigh Bates, Andrew Behling, Léa Bernard, Dylan Caverly, Alexandre Courtis, Philippe Decoste, Xavier Duchesne, Ella Godun, Anushka Goyal, Rik Keizer, Mathias Larrouturou, Leah Lavoie, Jana Mouchaimech, Dan-Cornelius Savu, Taj Sobral, Emma Sinasac, Arnab Sinha, and Maximilian Van der Wee.

    This work was funded by the Natural Sciences and Engineering Research Council of Canada (NSERC) Canada Graduate Scholarships — Master's (CGS-M) program and the McGill Summer Undergraduate Research in Engineering (SURE) program.

\end{plainchp}